### 2017-06-20 paper.tex

Despite the proven success of open-source and collaboratively developed lesson plans,
it is surprisingly uncommon in the traditional accademic setting.
Each year, thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some might use a common textbook written by a single author or two,
but besides that lecturers develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how much valuable time has been wasted,
and ultimately how the progress of post-secondary education has been held back by
the lack of community collaboration and sharing in this process.
This problem obviously extends beyond the university sector,
but it is curious that it is endemic in post-secondary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

@@

Micro-scale feedback can be gathered by an instructor while teaching a particular lesson.
Learners might provide feedback on things like typographical errors,
clarity/ease of quiz questions and/or the order in which topics are presented,
which the instructor can enter into a work-tracking system (e.g., GitHub issues) at the end of class.
As well as encouraging direct verbal feedback,
it's a good idea to provide learners with a means to provide feedback anonymously during class
(e.g., on small pieces of paper like sticky notes).

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These issues often relate to the fact that it can be difficult for lesson developers
to fully understand the frame of reference of their audience.
For instance, a lesson might inadvertently assume prior knowledge that many learners don't have,
which is information that can be collected in a survey.
If possible, it's a good idea to conduct the post-class survey 30--60 days after the fact.
This allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

@@

No single lesson can be right for every learner.
Two people with no prior knowledge of a specific subject
may still be able to move at very different speeds
because of different levels of general background knowledge.
Similarly,
lessons on ecology for learners in Utah and Florida
will probably be more relatable if they use different examples.
Equally,
no lesson development community can serve all purposes.
Some groups may prioritize rapid evolution,
while others may prefer a ``measure twice, cut once'' approach.

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this
even if contributors \emph{don't} disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one \cite{choral-explanations}.

But sometimes choices must be made.
The open source software community has wrestled with these issues for three decades,
and has evolved some best practices to handle them
\cite{producing-oss}.
As discussed in Rule~5,
the first step is to have a clear governance structure and a clear, permissive license.
Minor disagreements should be discussed openly and respectfully.
If they cannot be resolved---i.e., if they turn out not to be so minor after all---then
contributors should split off and evolve the lesson in the way they see best.
(This is one of the reasons to have a permissive license.)

>>>>

Despite the proven success of open-source and collaboratively developed lesson plans,
it is uncommon in the traditional accademic setting.
Each year, thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use a common textbook written by a single author or two,
but besides that lecturers develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how much valuable time has been wasted,
and ultimately how the progress of post-secondary education has been held back by
the lack of community collaboration and sharing in this process.
This problem obviously extends beyond the university sector,
but it is curious that it is endemic in post-secondary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

@@

Micro-scale feedback can be gathered by an instructor while teaching a particular lesson.
Learners might provide feedback on things like typographical errors,
clarity/ease of quiz questions or the order in which topics are presented,
which the instructor can enter into a work-tracking system (e.g., GitHub issues) at the end of class.
As well as encouraging direct verbal feedback,
it's a good idea to provide learners with a means to provide feedback anonymously during class
(e.g., on small pieces of paper like sticky notes).

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These issues often relate to the fact that it can be difficult for lesson developers
to fully understand the frame of reference of their audience.
For instance, a lesson might inadvertently assume prior knowledge that learners do not have,
which is information that can be collected in a survey.
If possible, it's a good idea to conduct the post-class survey 30--60 days after the fact.
This delay allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

@@

No single lesson can be right for every learner.
Two people with no prior knowledge of a specific subject
may still be able to move at different speeds
because of different levels of general background knowledge.
Similarly,
lessons on ecology for learners in Utah and Florida
will probably be more relatable if they use different examples.
Equally,
no lesson development community can serve all purposes.
Some groups may prioritize rapid evolution,
while others may prefer a ``measure twice, cut once'' approach.

If there are complementary ways to explain something,
or points of view that can cohabit respectfully,
it may be possible to present them side by side.
There are good pedagogical reasons to do this
even if contributors \emph{do not} disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one \cite{choral-explanations}.

But sometimes choices must be made.
The open source software community has wrestled with these issues for three decades,
and has evolved some best practices to address them
\cite{producing-oss}.
As discussed in Rule~5,
the first step is to have a clear governance structure and a clear, permissive license.
Minor disagreements should be discussed openly and respectfully.
If they cannot be resolved---i.e., if they turn out not to be so minor after all---then
contributors should split off and evolve the lesson in the way they see best.
(This is one of the reasons to have a permissive license.)
